%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right

\namesection{Sheng-Yu}{Chiu}{ % Your name
\urlstyle{same}\url{http://github.com/m943040028} \\ % Your website, LinkedIn profile or other web address
\href{mailto:m943040028@gmail.com}{m943040028@gmail.com} % Your contact information
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

\section{Education}

\subsection{Sun Yat-Sen University}

\descript{MS in Computer Science}
\location{2005-2007}

%------------------------------------------------

\subsection{I-Shou University}

\descript{BS in Computer Science}
\location{2002-2005}

\sectionspace % Some whitespace after the section

\section{Links} 

Github:// \href{https://github.com/m943040028}{\bf m943040028} \\
LinkedIn:// \href{http://lnkd.in/Exzyne}{\bf sy.chiu} \\

\sectionspace % Some whitespace after the section

\section{Skills}

\subsection{Software Development}
Scrum \textbullet{} Continuous Integration \textbullet{} \\
Test Driven Development \textbullet{} Design Patterns

\subsection{Embedded Software}
Linux Kernel \textbullet{} MicroKernel Design \textbullet{} \\
Device Drivers \textbullet{} Hyperviosr \textbullet{} \\
BootLoader \textbullet{}

\subsection{OpenSource Tools}
STL \textbullet{} Boost \textbullet SQLAlchemy \textbullet \\
BaseX \textbullet{} Strace \textbullet{} Valgrind

\subsection{Architecture}
X86 \textbullet{} IBM Power \textbullet{} Arm(v5,v7)

\subsection{Version Control}
git \textbullet{} gerrit

\subsection{Programming}
\location{Experienced:}
C \textbullet{} C++ \textbullet{} Assembly \textbullet{} Java \textbullet{} Python
\location{Familiar:}
Shell \textbullet{} Android \textbullet{} SQLite \textbullet XQuery

\sectionspace % Some whitespace after the section

\section{Personal Project} 

\subsection{\href{https://github.com/m943040028/prex}{\bf Prex}}
\descript{Real-time MicroKernel for PPC}

\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

\section{Experience}

\runsubsection{MediaTek}
\descript{| Senior Software Engineer}

\location{Apl 2014 – Current | Hsintsu, Taiwan}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Linaro Assignee, focused on secure environment system software development on arm.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{International Business Machines (IBM)}
\descript{| Staff Software Engineer}

\location{Apl 2013 – Mar 2013 | Taipei, Taiwan}
\begin{tightitemize}
\item Working with IBM’s next-gen CPU simulator using Java. Focused on MMU translation which is a very important module in processor core.
\item Refactored a data-driven system modeling software within 3 month (using python, sqlalchemy and xquery). Acting as key developer who defines new software architecture that eliminated thousand lines of duplicated code, easier to add new feature and new platform.
\item Building continuous-integration environment by integrating Jenkins/Gradle.
\item Reduced software developers’ time to do software integration from a hour to several minutes by writing a tool that integrated IBM cmvc and git.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{High-Tech Corporation (HTC)}
\descript{| Senior Software Engineer}

\location{Mar 2012 – Mar 2013 | Taipei, Taiwan}
\begin{tightitemize}
\item Working in a small (5 people) team whose mission is to deliver a software stack that enabled our android phone product to extend secondary display to TV through wireless-link, and provided android compatible API that enabled our user to write dual-screen applications. Delivered components in native framework level.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{High-Tech Corporation (HTC)}
\descript{| Principal Software Engineer}

\location{Aug 2007 – Jan 2012 |Hsintsu, Taiwan}
\begin{tightitemize}
\item Linux Device driver development, integration and debugging. Focused on graphics, video/audio, usb, ethernet, flash based storage and i2c device drivers.
\item Co-work with hardware engineer to do new platform bring-up.
\item Developed Linux snapshot boot (conjunction with bootloader) which reduces system boot time by 70\%.
\item Implemented m2ts streaming program on an Android based set-top box. Enabled zero-copy decoding by integrating VLC MultiMedia framework with Ti Omap4 hardware codec and video pipelines hardware.
\item Porting Real time operating system to a PowerPC 405 based platform.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%\section{Awards} 

%\begin{tabular}{rll}
%2007 & Phi Tau Phi Scholastic Honor Society NSYSU
%\end{tabular}

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page
\end{minipage}
\hfill

%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page
%\section{HighLight}

%\begin{tightitemize}
%\item As a member of small, fast-paced and agile team, whose member came from Taiwan, India and America.
%\item Having experiences in scrum, continuous integration and test-driven development.
%\item I’m on my way to become Clean Coder. (I’m a fan of uncle Bob)
%\item Familiar with x86, power(server) and arm(v5,v7) architecture.
%\item Experienced in Low Level Firmware design and implementation.
%\item Expertise to Linux Kernel and Device Driver development.
%\item Knowledge to MicroKernel-based kernel/hypervisor design, such as minix, l4ka, nova.
%\item Android native framework development experience. (multimedia and display)
%\end{tightitemize}

%\end{minipage} % The end of the left column

\end{document}
